---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nemo

`nemo` finds the [largest empty circle](https://www.cs.swarthmore.edu/~adanner/cs97/s08/papers/schuster.pdf) in the plane whose interior does not overlap with any given obstacles.
`nemo` includes ony two functions : 

- `nemo_hull` computes a concave hull from a set of points and is basically imported from package [concaveman](https://github.com/mapbox/concaveman) brought in R by [joelgombin](https://github.com/joelgombin/concaveman)
- `nemo_circle` computes the larget circle  inside a hull and which doesn't include any point : its center will be the point nemo

## Installation

You can install the development version from [GitHub](https://github.com/mtmx/nemo) with:

``` {r eval=F}
## install {remotes} if not already
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}
## install nemo for github
remotes::install_github("mtmx/nemo")
```
 

## Example

A basic example to find the largest empty circle inside a set of points and its center aka the point nemo :

```{r example , eval=T, echo=T, message=F}
library(nemo)
data(points)
hull_pts <-
nemo_hull(points = points %>% st_transform(2154),
            concavity =2,
            length_threshold = 10)

nemo_pts <-
nemo_circle(points = points %>% st_transform(2154),
            hull = hull_pts %>% st_buffer(dist=500),
            strict_inclusion = T,
            nmax_circles = 1)

# mapping output
library(ggplot2)

ggplot() +
  geom_sf(data = hull_pts %>% st_buffer(dist=500)  , size = 0.2) +
  geom_sf(data = nemo_pts ,
          size = 1,
          fill=NA,
          color = "red") +
  geom_sf(data = nemo_pts %>% st_centroid() ,
             size = 1,
             col = "red") +
  geom_sf(data=points %>% st_transform(2154))


```
